%-------------------------------------------------------------------------------
% File: hadoop.tex
%       
%
% Author: Marco Pinna
%         Created on 14/06/2022
%-------------------------------------------------------------------------------
\chapter{Hadoop}\label{ch:hadoop}
The first version was implemented in Java, using the Hadoop framework.\\
The directory structure of the project is the following:\\
\dirtree{%
.1 hadoop.
.2 main/java/it/unipi/hadoop.
.3 BloomFilter.java.
.3 MapRedComputeParams.java.
.3 MapRedBloomFilter.java.
.3 MapRedFalsePositiveRate.java.
.3 Util.java.
}
\hfill \break
\begin{itemize}
\item The \texttt{BloomFilter.java} class contains the implementation the Bloom filter.\\
The \textit{bitArray} structure of the Bloom filter was realized by using the \texttt{BitSet} class available in the \texttt{java.util.BitSet} Java library. It already comes with built-in methods for setting/resetting all the bits, performing bit-wise operations on it and serializing/deserializing the array.
The family of hash functions that was used --- as requested in the specifications --- is MurmurHash, which can be found in the \texttt{org.apache.hadoop.util.hash.MurmurHash} Java library.\\
\item The \texttt{MapRedComputeParams.java} class is used to compute the optimal filter parameters according to the constraints passed as input via command line.\\
\item The \texttt{MapRedBloomFilter.java} is the main class that contains all the MapReduce logic for the creation of the Bloom filters. It contains both the versions of the algorithm: the one \textit{withIndexes} and the one \textit{withBloomFilters}. One can toggle between the two by simply changing one command line argument when launching the program on the cluster.\\
\item The \texttt{MapRedFalsePositiveRate.java} is used to test the Bloom filters created by the previous class and check if the empirical FPR is actually consistent with the theoretical one that was yielded by \texttt{MapRedComputeParams.java} and used by \texttt{MapRedBloomFilter.java}.\\
\item The \texttt{Util.java} class contains constants and utility functions that are used in the rest of the code, such as the ones for parsing and splitting the input rows.\\
\end{itemize}

In the implementation of all the MapReduce classes, \texttt{setup()} and \texttt{cleanup()} methods were used: \texttt{setup()} to fetch the necessary parameters and initialize the data structures and \texttt{cleanup()} to emit the data collected during the previous elaborations.
\hfill \break
All the \texttt{MapRed*} classes take, as command line argument --- among the other parameters, the size of the split to be given as input to each mappers (i.e. the \texttt{num\_lines\_per\_split} argument); this parameter directly controls the number of mappers that are instantiated during the Map phase. To do this, the \texttt{NLineInputFormat} class was used, as required by the specifications, which can be found in the \texttt{org.apache.hadoop.mapreduce.lib.input.\\NLineInputFormat} Java library.\\
\hfill \break

\subsection*{Usage}\label{sub:usage}
The three \texttt{MapRed*} classes can be run with the following commands:\\

\begin{lstlisting}[basicstyle=\ttfamily\footnotesize, breaklines=true, backgroundcolor = \color{lightgray}]
hadoop jar it/unipi/hadoop/BloomFilter/1.0/BloomFilter-1.0.jar it.unipi.hadoop.MapRedComputeParams title.ratings.tsv output 0.01 157000
\end{lstlisting}
\hfill \break
\texttt{title.ratings.tsv} is the input file, \texttt{output} is the name of the output file, \texttt{0.01} is the desired value for the FPR \textit{p} and \texttt{157000} is the size of the partition to be handled to each mapper.
\vspace{5pt}
\hrule
\vspace{6pt}
\begin{lstlisting}[basicstyle=\ttfamily\footnotesize, breaklines=true, backgroundcolor = \color{lightgray}]
hadoop jar it/unipi/hadoop/BloomFilter/1.0/BloomFilter-1.0.jar it.unipi.hadoop.MapRedBloomFilter title.ratings.tsv output 157000 24404 63482 171928 420900 990060 2117062 3578304 3406703 1092505 156103 7 WithBloomFilters
\end{lstlisting}
\hfill \break
\texttt{title.ratings.tsv} is the input file, \texttt{output} is the name of the output file, \texttt{157000} is the size of the partition to be handled to each mapper, the ten numbers that follow are the values for \textit{m} for each filter, \texttt{7} is the value for \textit{k} and \texttt{WithBloomFilters} is a flag that toggles which of the two implementations is to be run.
\vspace{5pt}
\hrule
\vspace{6pt}
\begin{lstlisting}[basicstyle=\ttfamily\footnotesize, breaklines=true, backgroundcolor = \color{lightgray}]
hadoop jar it/unipi/hadoop/BloomFilter/1.0/BloomFilter-1.0.jar it.unipi.hadoop.MapRedFalsePositiveRateTest title.ratings.tsv testOutput 157000 output/part-r-00000 hadoop-namenode 9820
\end{lstlisting}
\hfill \break
\texttt{title.ratings.tsv} is the input file, \texttt{testOutput} is the name of the output file, \texttt{157000} is the size of the partition to be handled to each mapper, \texttt{output/part-r-00000} is the file from which the saved Bloom filters have to be read, \texttt{hadoop-namenode} is the host and \texttt{9820} is the port.\\
\hfill \break
The decision to set the partition size to 157000 was taken following the best-practice of assigning 1-1.5 cores to each mapper process; since the cluster that was used for testing had a total of 8 cores and the dataset had approximately 1.2M lines, 157000 was a suitable size for each partition. A more in-depth analysis on this parameter and its effects on the Key Performance Indexes is carried out in chapter \ref{ch:performance}.\\
\subsection*{Test}\label{sub:testHadoop}
The BloomFilters were tested in order to obtain a \textbf{false positive rate of 0.01}. The results are the following:\\

\renewcommand{\arraystretch}{1.5}
\begin{center}
	\begin{tabular}{|c | r | r | c | c |} 
		\hline
		\textbf{Bloomfilter Index} & \multicolumn{1}{c|}{\textbf{n}} & \multicolumn{1}{c|}{\textbf{m}} & \textbf{k} & \textbf{p} \\ 
		\hline
		1 & 2546 & 24404 & 7 & 0.0097\\ 
		\hline
		2 & 6623 & 63482 & 7 & 0.0101\\
		\hline
		3 & 17937 & 171928 & 7 & 0.0101 \\
		\hline
		4 & 43912 & 420900 & 7 & 0.0102\\
		\hline
		5 & 103292 & 990060 & 7 & 0.0101\\
		\hline
		6 & 220871 & 2117062 & 7 & 0.0100 \\ 
		\hline
		7 & 373321 & 3578304 & 7 & 0.0102\\ 
		\hline
		8 & 355416 & 3406684 & 7 & 0.0100\\ 
		\hline
		9 & 113980 & 1092505 & 7 & 0.0102\\ 
		\hline
		10 & 16286 & 156103 & 7 & 0.0101\\ 
		\hline
	\end{tabular}
\end{center}

